Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex

When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses\raft{Jessie: what are the best cites here? AA15?}.
Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an supoptimal target prediction.
\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}
% For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
% However, optimizing over a target loss is often a computationally hard problem.
% This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
% A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
% This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
% Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.

>>>>

When given a discrete target loss, such as for classification-like problems, direct empirical risk minimization is typically NP-hard, forcing one to find a more tractable surrogate.
To ensure consistency, the literature has embraced the notion of \emph{calibration} due to~\citet{tewari2007consistency}, and its generalizations to arbitrary discrete target losses\raft{Jessie: what are the best cites here? AA15?}.
Calibration is a much more tractable and weaker condition than consistency, yet the two are equivalent under suitable assumptions~\cite{tewari2007consistency,ramaswamy2016convex}.
Intuitively, calibration says that one cannot approach the optimal surrogate loss while linking to an suboptimal target prediction.
%\raft{FYI Jessie: what you had was now pretty redundant to what we have earlier}\jessie{Definitely}

% For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
% However, optimizing over a target loss is often a computationally hard problem.
% This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss.%, or property we want to predict, as is more common in the the continuous estimation setting.
% A surrogate is no good on its own; we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
% This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
% Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\citet{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.
